\begin{resuingles}
Chagas disease is a tropical parasitic disease caused by the protist Trypanosoma cruzi, it is considered by the World Health Organization as a neglected tropical disease. Neglected tropical diseases are those that affect a high amount of the population, mostly on third world countries, and have an expensive, inefficient or inexistent treatment. The first step in determining the effectiveness of new antichagasic drugs that help reduce the costs of treating the disease is the counting of the intracellular parasitic form (amastigote) under a microscope.
The watershed transform is an image segmentation algorithm.
Image segmentation is the process of partitioning a digital image into its constituent regions. Said segmentation is an important process to perform a count of Trypanosoma cruzi amastigotes and thus determine the efficacy of new antichagasic drugs.The watershed algorithm has been used in to solve the segmentation problem, most often in grayscale images. Grayscale images may lose important information for segmentation, this is because it only uses the intensity of the colors. The color images give more information, but implementing the color watershed transform is not trivial. The implementation of the watershed transform by flooding in color images proposed by Meyer, requires an order between the pixels to perform the segmentation. This work extends the watershed algorithm by flooding for color images using the CIELab color space for the segmentation of Trypanosoma Cruzi Amastigotes in microscopic cell images. It uses the Euclidean distance to a reference color for the ordering of the pixels. The proposed method was compared with the implementation of the watershed transform in different color spaces and using different pixel ordering methods. The CIELab color space using the distance to the median of the colors presented the best results with an accuracy of 91 \%. The CIELab color space obtained better results regardless of the reference color used in relation to the methods in the different color spaces and grayscale images. The proposed segmentation method can be used to identify Trypanosoma cruzi amastigotes, and in this way can count and collect statistics necessary to produce new drugs for Chagas disease.

\end{resuingles}


